---
title: "SSA Vic & Tas Di Cook Award"
description: |
  Open-Source Statistical Software Award by Statistical Society Australia, Victorian & Tasmanian Branch
site: distill::distill_website
output: 
  distill::distill_article:
    includes:
      before_body: assets/banner.html
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
```




# <i class="fas fa-bullhorn"></i> Call for Submission

## Eligibility

1. The Award is open to students, or students who graduated within one year of the application due date, of Victorian or Tasmanian educational institutes only. 
1. The Award is not open to any work that has won another software competition or award, although the applicant may submit separate work that is significantly different to any previously winning work. 
1. The applicant must have begun the development while enrolled as a student. 
1. The applicant does not need to be an SSA member to apply for this award. 
1. Individuals or teams are eligible to participate in this competition. 
1. If the software development was a team effort, the major contribution should be that of the students. 
1. The submitted software must be open-source and actively maintained at the time of entry.

## Criteria

The applicant must submit:

* A brief description of the importance of the software to statistical practice and discuss the advantages and disadvantages of the new contribution compared to existing implementations. Up to 400 words.
* An installable software product (e.g. package or web app) with its source code for use by the judging panel. It should be accompanied by enough information to allow the judges to effectively use and evaluate the software (including its design considerations). This information can be provided in a variety of ways, including but not limited to: a user manual, a manuscript, a website, or an online help resource for the package.
* For team developers, a letter endorsing that the majority of the software development was done by the student(s).

The applicant may also optionally submit:

* Any evidence of potential impact and usefulness to the community. 
* Any accepted paper(s) related to the software. 
* A written tutorial demonstrating the use of the software product with a limit of 4000 words that can be shared on this website.



All of these items should be submitted by completing the application form under [Forms](#forms) before the application deadline. All submitted materials must be in English. 


## Judges & Assessors

1. Assessors will be drawn from expert statistical software developers who are not entrants in the current round. 
1. Assessors will be preferably drawn from outside of Victoria and Tasmania. 
1. Assessors give input by completing the assessor form similar to the one supplied under [Forms](#forms).
1. The judging panel will comprise committee members of the [Statistical Computing and Visualisation Section of the Statistical Society of Australia](https://www.statsoc.org.au/Statistical-Computing-and-Visualisation-Section) or other members selected by the SSA Vic & Tas council.
1. Assessors for this competition will be decided after close of submission upon consultation with the judging panel.
1. A judging panel will collate assessors input to decide on the winner. 
1. The decision of the judging panel is final.

If you would like to be an assessor, please email vic.branch@statsoc.org.au along with your software expertise. 


## Forms

<ul class="fa-ul">
  <li><span class="fa-li"><i class="fas fa-file-code"></i></span>[Application form](https://docs.google.com/forms/d/e/1FAIpQLScM2zw-z3TiLxpCiVa3ex-5hEItv9y8XZySIMfQomQmA8hO5A/viewform?usp=sf_link)</li>
  <li><span class="fa-li"><i class="fas fa-gavel"></i></span>[Assessor form](assessor-form.pdf)</li>
</ul>


# <i class="fas fa-calendar-alt"></i> Important Dates

```{r date, echo = FALSE}
tribble(~Date, ~What,
        "Mon 2nd Oct 2023", "Opening of submissions",
        "<strike>Fri 24th Nov 2023</strike> Fri 8th Dec 2023", "Close of submissions",
        "March 2024 meeting", "Announcement of the award winner") %>% 
  knitr::kable()
```



# <i class="fas fa-trophy"></i> Prize

The awardee will receive a cash prize of $1,000 and an opportunity to present their work at an event planned in 2024.

All applications of sufficient quality will have their tutorial (if supplied) made available on the website (https://statsocaus.github.io/dicook-award/) with its introduction and link to the tutorial circulated to SSA Vic members and other avenues. 


